### 2017-05-12 paper/evaluation.tex
update evaluation table
update table
update scalability plot

This experiment evaluates the impact of making available to the build
system a growing number of CPUs for testing.  For that reason, we used
a more poweful machine. \Fix{...describe machine...}  We focused on
configuration \ForkSeq{}
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.2\textwidth]{R/scalability/scalability.pdf}
    \caption{\label{fig:scalability}Scalability.}
\end{wrapfigure}
as the goal of this experiment is to evaluate the impact of spawning a
growing number of JVMs, running on different CPUs.  Furthremore, we
selected the subject \subjectScalability{} as it represents the case
of a long-running test suite (see Figure~\ref{tab:speedup}) with test
cases distributed across many test classes (\Fix{X} test classes for
\subjectScalability{}).  Note that a test class is the smallest unit
that can be used to spawn a test job on a JVM and that we have no
control over which test classes will be assigned to which JVM that the
build system forks.

@@

\begin{figure*}[t]
\centering
\small
\begin{tabular}{l|rr|rrrrrrrrrr}
\toprule
\multirow{2}{*}{\emph{Subject (module)}} & \multicolumn{2}{c|}{\emph{\Seq}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T_\text{cost} $ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
Jankotek MapDB  & \entry{8.2m}{5324} & \entry{1.52x}{0\%} & \entry{2.73x}{0\%} & \entry{4.82x}{0.05\%}   & \entry{}{} & \entry{}{}\\%
Stripe Java     & \entry{4.3m}{302}  & \entry{4.78x}{6.31\%} & \entry{3.31x}{7.31\%} & \entry{21.50x}{14.95\%} & \entry{}{} & \entry{}{}\\%

@@

GoogleCloud Dataflow Java (\CodeIn{sdk}) & \entry{1.6m}{3345}  & \entry{1.23x}{1.67\%} & \entry{2.67x}{1.05\%} & \entry{0.80x}{5.35\%} & \entry{}{} & \entry{}{}\\%

Javaslang (\CodeIn{core})     & \entry{1.1m}{17513}  & \entry{1.38x}{0\%} & \entry{1.83x}{0\%} & \entry{1.38x}{0\%} & \entry{}{} & \entry{}{}\\%
%%  & \entry{x.xm}{0}  & \entry{}{\%} & \entry{}{\%} & \entry{}{\%} & \entry{}{} & \entry{}{}\\%
%%OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
%%Apache Flume (\CodeIn{core}) &  \entry{7.7m}{392}  & \blankentry{}        & \blankentry{}        & \blankentry{}       & \entry{0.9x}{0\%} & \blankentry{} \\%
%%Facebook Archive Linkbench   &  \entry{4.5m}{98}   & \entry{1.0x}{0.2\%}  & \entry{1.6x}{1.2\%}       & \entry{1.0x}{0\%}  & \entry{1.7x}{0.5\%}  & \entry{1.7x}{0.2\%}\\%
%%AWS SDK Java (\CodeIn{core}) &  \entry{3.8m}{847}  & \multicolumn{6}{c}{\Fix{requires investigation}} & \entry{2.2x}{0.1\%} & \entry{3.2x}{2.0\%}\\%

>>>>

This experiment evaluates the impact of making available to the build
system a growing number of CPUs for testing.  For that reason, we used
a more poweful machine. \Fix{...describe machine...}  We focused on
configuration \ForkSeq{}
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.2\textwidth]{R/scalability/scalability.pdf}
    \caption{\label{fig:scalability}Scalability.}
\end{wrapfigure}
as the goal of this experiment is to evaluate the impact of spawning a
growing number of JVMs, running on different CPUs.  Furthremore, we
selected the subject \subjectScalability{} as it represents the case
of a long-running test suite (see Figure~\ref{tab:speedup}) with test
cases distributed across many test classes (194 test classes for
\subjectScalability{}).  Note that a test class is the smallest unit
that can be used to spawn a test job on a JVM and that we have no
control over which test classes will be assigned to which JVM that the
build system forks.

@@

\begin{figure*}[t]  
\centering
\small
\setlength{\tabcolsep}{5pt}
\begin{tabular}{l|rr|rr|rr|rr|rr|rr}
\toprule
\multirow{2}{*}{\emph{Subject (module)}} & \multicolumn{2}{c|}{\emph{\Seq}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T_\text{cost} $ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
Jankotek MapDB  & \entry{8.2m}{5,324} & \entry{1.52x}{0\%} & \entry{2.73x}{0\%} & \entry{4.82x}{0.05\%}   & \entry{}{} & \entry{}{}\\%
Stripe Java     & \entry{4.3m}{302}  & \entry{4.78x}{6.31\%} & \entry{3.31x}{7.31\%} & \entry{21.50x}{14.95\%} & \entry{}{} & \entry{}{}\\%

@@

GoogleCloud Dataflow Java (\CodeIn{sdk}) & \entry{1.6m}{3,345}  & \entry{1.23x}{1.67\%} & \entry{2.67x}{1.05\%} & \entry{0.80x}{5.35\%} & \entry{}{} & \entry{}{}\\%

Javaslang (\CodeIn{core})     & \entry{1.1m}{17,513}  & \entry{1.38x}{0\%} & \entry{1.83x}{0\%} & \entry{1.38x}{0\%} & \entry{}{} & \entry{}{}\\

RipMe                         & \entry{1.1m}{54}  & \entry{0.94x}{0\%} & \entry{1.63x}{0\%} & \entry{1.63x}{0\%} & \entry{1.37x}{0\%} & \entry{1.42x}{0\%}\\

JCabi Github                  & \entry{2.6m}{634} & \entry{2.1x}{0\%} & \entry{17.7x}{0\%} & \entry{28.8x}{0\%} & \entry{}{} & \entry{}{} \\

	Moquette & \entry{3.5m}{x} & \entry{4.2x}{x} & \entry{2.9x}{} & \entry{13.5x}{} & \entry{}{} & \entry{}{} \\

\midrule

\textbf{Average}   & \entry{-}{-} & \entry{-}{-} & \entry{-}{-} & \entry{-}{-}
& \entry{-}{-} & \entry{-}{-} \\%

%%  & \entry{x.xm}{0}  & \entry{}{\%} & \entry{}{\%} & \entry{}{\%} & \entry{}{} & \entry{}{}\\%
%%OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
%%Apache Flume (\CodeIn{core}) &  \entry{7.7m}{392}  & \blankentry{}        & \blankentry{}        & \blankentry{}       & \entry{0.9x}{0\%} & \blankentry{} \\%
%%Facebook Archive Linkbench   &  \entry{4.5m}{98}   & \entry{1.0x}{0.2\%}  & \entry{1.6x}{1.2\%}       & \entry{1.0x}{0\%}  & \entry{1.7x}{0.5\%}  & \entry{1.7x}{0.2\%}\\%
%%AWS SDK Java (\CodeIn{core}) &  \entry{3.8m}{847}  & \multicolumn{6}{c}{\Fix{requires investigation}} & \entry{2.2x}{0.1\%} & \entry{3.2x}{2.0\%}\\%
